---
title: "Eenie Meenie Miney Mo - Where Should I Go?"
author: "Vivian Duong"
---

## Motivation and Context

-   we're college students –\> maybe in near future, we need to find a place to stay for work, other school things, personal reasons, etc...

-   rent searching is hard enough already –\> skip some of the hard work w/ these things! this is somewhat of a personal project b/c i have my own plans to move out soon :0

```{r}
#| label: do this first
#| echo: false
#| message: false

# change this to the location of your Quarto file containing your project; then delete this comment
library(readr)
here::i_am("project1/math-237-project_template.qmd")
socalrent <- read_csv(here::here("project1/socal_raw.csv"))
```

## Main Objective

-   automate some of the work we need to do when deciding on a place to stay !
    -   finding the "best" deal

## Packages Used In This Analysis

```{r}
#| label: load packages
#| message: false
#| warning: false

library(here)
library(tidyverse)
library(janitor)
library(broom)
```

| Package | Use |
|--------------------------------|----------------------------------------|
| [here](https://github.com/jennybc/here_here) | to easily load and save data |
| [readr](https://readr.tidyverse.org/) | to import the CSV file data |
| [sf](https://r-spatial.github.io/sf/) | to import and work with geojson files |
| [jsonlite](https://jeroen.r-universe.dev/jsonlite) | to work with json files |
| [dplyr](https://dplyr.tidyverse.org/) | to massage and summarize data |

## Design and Data Collection

-   collected w/ Nathalie in class from RedFin, compiled onto google sheets / microsoft excel –\> csv file

```{r}
#| label: preview dataset

socalrent |>
  head() # so far so good, data looks ok except the 3 empty columns

socalrent |>
  slice(265:266, 275:278) # some unusual observations... gotta clean that up

socalrent |>
  group_by(County, Type) |>
  count()

socalrent |>
  filter(
    Type == "house",
    Beds <= 1
  )
```

## Data Massaging

```{r}

```

## Exploratory Data Analysis

## Modeling (Optional Section)

## Conclusion

### Limitations

-   data collection / scraping off sites... difficult/tedious depending on OS used (Mac vs Windows)

-   data collected limited to "recommended" hits on Zillow (? dbl chk w/ Nat what site we used...)

-   only provides so much info and can only do so much work ... other variables and processes assoc. w/ rent not accounted for

-   intention for this project was to mainly avoid the math stuff of rent searching...

-   everyone's preferences are different when looking for a place to stay !

### Reflection (Optional Subsection)
